Syntax Is All You Need: A Universal-Language Approach to Mutant Generation

### 2023-03-29 paper/main.tex
Updating numbers for Java

pebble & 85 & 0.81 & 50\% & 20 & 0.95 & N/A & 8 & 1.00 0\% \\
... \\\midrule
\textbf{Mean} &  XX & XX & XX & XX & XX & XX & XX & XX & XX \\
\textbf{Std.Dev.} &  XX & XX & XX & XX & XX & XX & XX & XX & XX \\
\end{tabularx}
}
\end{table}

\begin{table}[htbp]
\centering
{\small
\caption{Python (Our Implementation vs. Mutmut vs. CosmicRay)}
\label{tab:table_python2}
\begin{tabularx}{\columnwidth}{l|rrr|rrr|rrr}
\toprule
                 & \mc{3}{c|}{Comby}   & \mc{3}{c|}{MutMut} & \mc{3}{c}{CosmicRay} \\
\textbf{Project} & \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv}
& \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv} 
& \textbf{Mutants} &  \makecell{\textbf{Mutation} \\ \textbf{Score}} & \textbf{\% Eqv} \\ \midrule
keract  & & & & & & & \\
\textbf{Mean} &  XX & XX & XX & XX & XX & XX & XX & XX & XX \\
\textbf{Std.Dev.} &  XX & XX & XX & XX & XX & XX & XX & XX & XX \\
\end{tabularx}
}
\end{table}

@@

\begin{table}[htbp]
\centering
{\small
\caption{Rust (Our Implementation vs. Cargo-Mutants)}
\label{tab:table_rust2}
\begin{tabularx}{\columnwidth}{X|crr|crr}
\hline
        & \multicolumn{3}{c|}{Comby}  & \multicolumn{3}{c}{cargo-mutants} \\ 
Project & Mutants & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} & Mutants & \makecell{\textbf{Mut.} \\ \textbf{Score}} & \textbf{\% Eqv.} \\[1ex]\midrule

cargo release & & & & & \\    
\textbf{Mean}   & FIXME & 0.29 & 16.67\% & FIXME & 0.33 & N/A\\
\textbf{Std. Dev} & FIXME & 0.37 & 13.66\%   & FIXME & 0.38 & N/A \\\bottomrule
\end{tabularx}}
\end{table}

>>>>

pebble & 85 & 0.81 & 20\% & 20 & 0.95 & N/A & 8 & 1.00 & 0\% \\
spring-hateoas & 176 & 0.37 & 0\% & 114 & 0.28 & N/A & 38 & 0.39 & 0\% \\
javacc & 503 & 0.21 & 0\% & 143 & 0.21 & N/A & 82 & 0.78 & 0\% \\
coffee-gb & 174 & 0.23 & 0\% & 36 & 0.89 & N/A & 29 & 0.38 & 0\% \\
egads & 622 & 0.71 & 10\% & 107 & 0.81 & N/A & 85 & 0.87 & 0\% \\
apk-parser & 338 & 0.08 & 0\% & 89 & 0.16 & N/A & 33 & 0.09 & 0\% \\
\midrule
\textbf{Mean} &  316.33 & 0.40 & 5.00\% & 84.83 & 0.55 & N/A & 45.83 & 0.59 & 0.00\% \\
\textbf{Std.Dev.} &  210.81 & 0.29 & 8.37\% & 47.60 & 0.37 & N/A & 30.93 & 0.35 & 0.00\%8
 \\
\end{tabularx}
}
\end{table}

@@
